\documentclass{scrartcl}

\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

\title{Semester 2 Review}

%Please do not change the subtitle
\subtitle{COMP110-5}

%Please put your student ID in the author field
\author{DH185421}

\begin{document}

\maketitle
\abstract{.}
\section{Introduction}
The final term of the year is nearing to the end and the time to review one self has come, the three skills I would like to work on are using time constructively, clear and concise speaking and academic reading.
\section{Using time constructively}
Firstly, time management or more specific using my time constructively has improved considerably but still needs to be worked on. The way this affected my quality of work is by not putting enough time into doing the work, by leaving work to only a week or two before the hand in I would work on other tasks and only put little time into that piece of work and vice versa. This became even more of a challenge the more work piled up as it made me become flustered and discombobulated, during this I would procrastinate and keep putting it off. To work on improving this I will be going to the FXU ask team to have a meeting on ways to improve time management, another planned method is to print out a monthly deadline sheet where each month I put on when my deadlines are due and plan out a week by week work time plan.

\section{Clear and concise speaking}
Presentational skills are an important life skill especially in the workplace, having good presentational skills is key for you to get your message across to the other person(s). In the course there has been a few times where I need to stand in front of the class and present to, this is one of many times good presentational skills are good here. A clear talk can let your tutors and classmates know exactly what you are talking about but because my presentational skills aren't that great they were not understanding my points. The main way for me to improve my presentational skills is to practice, practice is the main way for me to get better at speaking, each week I should ask a few friends to listen to me speak about the work I have been doing. This will allow me to become more confident in my speaking and they can offer advice if I speak to fast or my speech is mumbled.

\section{Academic reading}

Lastly, the final skill I would like to work on is academic reading. I found that I would only be reading when the course demands it. Not reading general academic posts/journals regularly nullifies the broadening of intellectual thinking, when it comes to reading for the course not as much information is retained to say if I read on a regular basis. A way of improving this is by setting myself a number of articles I need to read in a week, my tutor also posts useful information on the course page which would help me to start off with. I would also like to see if at the end of each week to see how much I remember of that article and then check back and see if I am correct.

\section{Conclusion}
With different goals in mind to work on for next year I will be using the ways listed above to start to improve my work ethic. I am confident I will be able to achieve them.
\end{document}